---
title: "Econ_Assignment_4"
author: "Callie Steffen,"
date: "5/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
abate<-read.csv("HW4.csv")
library(tidyverse)
library(ggplot2)

```
Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give you a model of the marginal cost of abatement function for each sector. How well do your models fit the data for each sector? You may need to experiment with different functional forms. Produce a plot of the estimated marginal abatement cost functions in all four sectors (this plot should go in your memo).


```{r}
a<-ggplot(abate,aes(x=Abatement, y=MC_A))+ ##Linear
  geom_point()
sectorA<-lm(data=abate, MC_A~Abatement)
summary(sectorA)

sectorA_fxn=function(x){sectorA$coefficients[2]*x +sectorA$coefficients[1]}

SectorA_Intercept<-sectorA$coefficients[1]
SectorA_Abatement<-sectorA$coefficients['Abatement']

b<-ggplot(abate,aes(x=Abatement, y=MC_B))+ 
  geom_point()

sectorB<-lm(data =abate, MC_B~Abatement)
summary(sectorB)

SectorB_Intercept<-sectorB$coefficients[1]
SectorB_Abatement<-sectorB$coefficients['Abatement']


c<-ggplot(abate,aes(x=Abatement, y=MC_C))+ ##Linear
  geom_point()
sectorC<-lm(data=abate, MC_C~Abatement)
summary(sectorC)

SectorC_Intercept<-sectorC$coefficients[1]
SectorC_Abatement<-sectorC$coefficients['Abatement']

d<-ggplot(abate,aes(x=Abatement, y=MC_D))+ ##NonLinear
  geom_point()
sectorD<-lm(data = abate, MC_D~Abatement)
summary(sectorD)

SectorD_Intercept<-sectorD$coefficients[1]
SectorD_Abatement<-sectorD$coefficients['Abatement']



marginal_graph <- ggplot(abate) +
  geom_smooth(aes(Abatement,MC_A, color="Sector A"), method=lm,se=FALSE) +
  geom_smooth(aes(Abatement,MC_B,color=" Sector B"), method=lm, se=FALSE) +
  geom_smooth(aes(Abatement,MC_C, color="Sector C"), method=lm, se=FALSE) +
  geom_smooth(aes(Abatement,MC_D, color="Sector D"), method=lm, se=FALSE) +
  labs(x = "CO2 (Tons)", y = "Cost ($)") +
  theme_classic()+
  theme(legend.title = element_blank())
  


##Does it plot LM or jsut columns against each other? #### LOOK AT R^2

marginal_graph



```


2. Using these models and the current level of carbon emissions, derive each sector’s demand curve for carbon emissions. In other words, how much would each sector be willing to pay for the right to pollute the first unit, second unit, etc? Draw these demand curves on a graph. Which sector is willing to pay the most for the first unit of carbon emissions?

```{r}


###Have to find y intercept to find demand curve
##y=mx+b Solve for y
##y=slope(abatement)*x(given)+intercept(calculated from summary)

y_a=SectorA_Abatement*180 + SectorA_Intercept # (0,95.2) (180,0)

y_b=SectorB_Abatement*200 + SectorB_Intercept # (0,49.1) (200,0)

y_c=SectorC_Abatement*220 + SectorC_Intercept #(0,161) (220,0)

y_d=SectorD_Abatement*300 + SectorD_Intercept #(0,87.7) (300,0)

###Price^

##coefficients for current carbon

a=180
b=200
c=220
d=300

##NOW LETS FIND THE DEMAND CURVES NOW THAT WE HAVE Y
##DEMAND CURVES ARE "WILLINGNESS TO PAY"

a_demand = function(x) {
  Demand = (-95.2/180)*x + SectorA_Intercept
}

b_demand= function(x) {
  Demand = (-49.1/200)*x + SectorB_Intercept
}

c_demand = function(x) {
  Demand = (-y_c/c)*x + SectorC_Intercept
}

d_demand = function(x) {
  Demand = (-y_d/d)*x + SectorD_Intercept
}



##graph the demand curves BUT HOW?!


graph_functions <- ggplot(data.frame(x=c(0,300), y=c(0,200)), aes(x=x, y=y))+
  stat_function(fun=a_demand, color="blue")+
  stat_function(fun=b_demand, color="green")+
    stat_function(fun=c_demand, color="orange")+
  stat_function(fun=d_demand, color="pink") +
  scale_x_continuous(expand = c(0,0), breaks=seq(0,500, by=50)) +
  scale_y_continuous(expand = c(0,0)) +
  theme_classic()

graph_functions

##SECTOR C willing to Pay the MOST!

##is the graph right?
##how to calculate total cost if its below 0
##


```


3. Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. For each of the policy options listed below, derive: (1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated.

A) POLICY A: Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus reducing total emissions from 600 down to 300).

```{r}

### POLICY OPTION A:

#1) total cost of meeting the target in Country X (sectors A, B, C added together, find each triangle and add up)

SA_CA = function(x){
  (sectorA$coefficients[2]*x +sectorA$coefficients[1])
} # carbon tax is $114.04 -- confirm!

SA_CA(114.04) # tells us what? the Q emitted under the tax for sector A?

SB_CA = function(x){
  (sectorB$coefficients[2]*x +sectorB$coefficients[1])
}
SC_CA = function(x){
  (sectorC$coefficients[2]*x +sectorC$coefficients[1])
  }


#2) The cost OR benefit to each sector (do this part first! each sector)

#??? how can we get acutal numbers for the cost to each sector?

costA = integrate(a_demand, 0, 100)
costB = integrate(SB_CA, 0, 100)
costC = integrate(SC_CA, 0, 100)
country_TC_A = costA$value + costB$value + costC$value  


```


B) POlICY B: Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.

```{r}

### POLICY OPTION B:

##tax on carbon by using aggregate demand 

#aggregate abatement curve


agg_step1<- (1/SectorA_Abatement+1/SectorB_Abatement+1/SectorC_Abatement)/3
new_intercept<- ((sectorA$coefficients[1]/-sectorA$coefficients[2])-SectorB_Intercept/SectorB_Abatement +SectorC_Intercept/-SectorC_Abatement)/3
agg_abatement <- function(x){(x+(-new_intercept))/agg_step1}
price_carbon <- function(x){agg_abatement(300)}

price_carbon(300) # carbon tax is $114.04 -- confirm!

#plug (300) into agg abatement to get price: 114.0445

#1) total cost of meeting the target in Country X  # tells us what? the Q emitted under the tax for sector A?

#?????


#2) The cost OR benefit to each sector

# Find the intersection of A curve & price of carbon
intersectA<-curve_intersect(price_carbon, ??????? , empirical = FALSE, domain=c(0,300)) 

# Find the intersection of A curve & price of carbon
intersectB<-curve_intersect(price_carbon(), ???, empirical = FALSE, domain=c(0,300)) 

# Find the intersection of A curve & price of carbon
intersectC<-curve_intersect(price_carbon, ????, empirical = FALSE, domain=c(0,300)) 

#3) The tax revenue generated

```

C) POLICY C: Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three sectors are allowed to trade with each other. You will need to derive the outcome of that trading.

```{r}

### POLICY OPTION C:

#1) total cost of meeting the target in Country X

#2) The cost OR benefit to each sector

#3) The tax revenue generated




```

